Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-22 paper/main.tex
updated descriptions of figures/analyses prior to implementing them

\section*{Results}
\begin{itemize}
\item characterizing behaviors (potentially broken down by 3--4
  fitness-defined categories, like activity level quartile; may also
  want to have separate figures: one for characterizing behaviors on
  average, and a second breaking down by fitness variable, e.g. after
  the correlation analyses are presented)
  \begin{itemize}
  \item Free recall: pfr, lag-CRP, spc
    \item Naturalistic recall: reproduce a version of the sherlock
      movie/recall trajectories
    \item Foreign language flashcards: p(correct) by activity level
      \item Spatial learning: mean error by number of shapes
      \end{itemize}
    \item Fitness info (break down by task performance, potentially
      separately for each task); also separate out recent (raw) and recent versus baseline
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations)
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline trends
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

>>>>

\section*{Results}
Before testing our main hypothesis, we first examined the behavioral
data from each memory task.  We expected that the general trends and
tendancies in the behavioral data would follow previously reported
behaviors from similar tasks that had been utilized in prior work.  We
were also interested in characterizing the variability in task
performance across participants.  For example, if all participants
exhibited near-identical behaviors or performance on a given task, we
would be unable to identify how memory performance varied with
mental health or exercise.

\begin{itemize}
\item characterizing behaviors (color by quartile and continue the
  color scheme in later figures-- hue reflects task, shading reflects
  performance.  white outline means immediate, black outline means delayed)
  \begin{itemize}
  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color: recall performance)
    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
      movie/recall trajectories (color: mean precision)
    \item Foreign language flashcards (immediate + delayed): p(correct) histogram (color: p(correct))
      \item Spatial learning: mean error by number of shapes (color:
        slope of line fit to errors as a function of the number of shapes)
      \end{itemize}
    \item Fitness info (break down by task performance, potentially
      separately for each task); also separate out recent (raw) and
      recent versus baseline -- color using same color scheme as
      behavior figure
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations)
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figure)
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}
